$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-05-11 paper/e6ssm-tuning-paper.tex
emphasise that the leading two loop corrections are for the light Higgs.

Using the approach outlined above, we are able to scan the low energy
parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
in each.  To do so, we implemented the above expressions for computing
the fine tuning in a modified version of the E$_6$SSM spectrum
generator that was used in \cite{Athron:2013ipa}.  This code
implemented two-loop RGEs for all parameters except the soft scalar
masses.  In order to properly include the fine tuning impact of the
$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,
  Staub:2010jh, Staub:2012pb, Staub:2013tta} and FlexibleSUSY
\cite{Athron:2014yba}, which also makes use of SOFTSUSY
\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses
are calculated including the leading one-loop effective potential
contributions given in \cite{Athron:2009bs} and the leading two-loop
contributions from \cite{King:2005jy} which are a generalsiation of
the correctsions in the MSSM and NMSSM calculated using effective
field theory techniques \cite{Carena:1995wu,Ellwanger:1999ji}.  To
scan over the MSSM parameter space, the equivalent MSSM fine tuning
expressions were implemented into a modified version of SOFTSUSY
3.3.10 \cite{Allanach:2001kg}.  For consistency with the results
produced in the $E_6$ models, and for computational speed, for our
main scans only the dominant one- and two-loop corrections to the
CP-even Higgs masses were included.  Finally, in all of the results
below the fine tuning was evaluated at the scale $Q =
M_{\textrm{SUSY}} = \sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where
$m_{\tilde{t}_{1,2}}$ are the running $\overline{\textrm{DR}}$ stop
masses evaluated at $Q = M_{\textrm{SUSY}}$.

>>>>

Using the approach outlined above, we are able to scan the low energy
parameter space of the MSSM and E$_6$SSM and calculate the fine tuning
in each.  To do so, we implemented the above expressions for computing
the fine tuning in a modified version of the E$_6$SSM spectrum
generator that was used in \cite{Athron:2013ipa}.  This code
implemented two-loop RGEs for all parameters except the soft scalar
masses.  In order to properly include the fine tuning impact of the
$SU(3)$ gaugino soft mass $M_3$, we have extended the original code to
make use of the two-loop RGEs generated by SARAH \cite{Staub:2009bi,
  Staub:2010jh, Staub:2012pb, Staub:2013tta} and FlexibleSUSY
\cite{Athron:2014yba}, which also makes use of SOFTSUSY
\cite{Allanach:2001kg, Allanach:2013kza}.  The CP-even Higgs masses
are calculated including the leading one-loop effective potential
contributions given in \cite{Athron:2009bs} and for the light Higgs we
use the leading two-loop contributions from \cite{King:2005jy} which
are a generalsiation of the correctsions in the MSSM and NMSSM
calculated using effective field theory techniques
\cite{Carena:1995wu,Ellwanger:1999ji}.  To scan over the MSSM
parameter space, the equivalent MSSM fine tuning expressions were
implemented into a modified version of SOFTSUSY 3.3.10
\cite{Allanach:2001kg}.  For consistency with the results produced in
the $E_6$ models, and for computational speed, for our main scans only
the dominant one- and two-loop corrections to the CP-even Higgs masses
were included.  Finally, in all of the results below the fine tuning
was evaluated at the scale $Q = M_{\textrm{SUSY}} =
\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$, where $m_{\tilde{t}_{1,2}}$
are the running $\overline{\textrm{DR}}$ stop masses evaluated at $Q =
M_{\textrm{SUSY}}$.
